---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# presentresults

<!-- badges: start -->
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)
[![check-standard](https://github.com/impact-initiatives/presentresults/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/impact-initiatives/presentresults/actions/workflows/check-standard.yaml)
[![Codecov test coverage](https://codecov.io/gh/impact-initiatives/presentresults/branch/main/graph/badge.svg)](https://app.codecov.io/gh/impact-initiatives/presentresults?branch=main)
<!-- badges: end -->

The goal of presentresults is to create outputs from a results table (long format with 
analysis key).

The analysis key is the unique identifier of the analysis. The format is the following:

- analysis type @/@ analysis variable %/% analysis variable value @/@ grouping variable %/% grouping variable value

- analysis type @/@ dependent variable %/% dependent variable value @/@ independent variable %/% independent variable value

If there are two or more grouping variables it would look like that

- analysis type @/@ analysis variable %/% analysis variable value @/@ grouping variable 1 %/% grouping variable value 1 -/- grouping variable 2 %/% grouping variable value 2

There are 3 types of separators:

- @/@ will separate the top level information: analysis type, the analysis (dependent) variable information and the grouping (independent) variable

- %/% will separate the analysis and grouping information: it will separate the variable name and the variable value

- -/- will separate 2 variables in case there are multiple variable in either the analysis or grouping sets.

The current analysis types available are :

- mean
- median
- prop_select_one: proportion for select one
- prop_select_multiple: proportion for select multiple
- ratio

## Installation

You can install the development version of presentresults from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("impact-initiatives/presentresults")
```

```{r load library}
library(presentresults)
```

## Large table variables (lines) per groups (columns)

This is how to turn a results table into a wide table variable per group.

```{r variable_x_group3stats}
example_variable_x_group <- presentresults_resultstable %>%
  create_table_variable_x_group()

example_variable_x_group[1:6, 1:9]
```

```{r, eval=FALSE}
example_variable_x_group %>%
  create_xlsx_variable_x_group(file_path = "mytable.xlsx")
```
The table without the higher and lower confidence bound.
```{r variable_x_group}
example_variable_x_group <- presentresults_resultstable %>%
  create_table_variable_x_group(value_columns = "stat")

example_variable_x_group[1:6, 1:9]
```


```{r, eval=FALSE}
presentresults_resultstable %>%
  create_table_variable_x_group() %>%
  create_xlsx_variable_x_group(
    file_path = "mytable.xlsx",
    value_columns = "stat"
  )
```

## Large table groups (lines) per variables (columns)

This is how to turn a results table into a wide group per variable. This format is made to be read 
in Excel.

```{r}
example_group_x_variable <- create_table_group_x_variable(presentresults_resultstable, value_columns = "stat")

example_group_x_variable[1:6, 1:10]
```
## Export a table group per variable in Excel

```{r, eval=FALSE}
presentresults_resultstable %>%
  create_table_group_x_variable() %>%
  create_xlsx_group_x_variable(file_path = "mytable.xlsx")
```

### Example for the IPC table

```{r}
example_ipc <- create_ipc_table(
  results_table = presentresults_resultstable,
  dataset = presentresults_MSNA_template_data,
  cluster_name = "cluster_id",
  fclc_matrix_var = "fcls_cat",
  fclc_matrix_values = c("phase_1", "phase_2", "phase_3", "phase_4", "phase_5"),
  fc_matrix_var = "fcm_cat",
  fc_matrix_values = c("phase_1", "phase_2", "phase_3", "phase_4", "phase_5"),
  with_fclc = TRUE,
  fcs_cat_values = c("low", "medium", "high"),
  rcsi_cat_values = c("low", "medium", "high"),
  lcsi_cat_var = "lcs_cat",
  lcsi_cat_values = c("none", "stress", "emergency", "crisis"),
  hhs_cat_var = "hhs_cat",
  hhs_cat_values = c("none", "slight", "moderate", "severe", "very_severe"),
  lcsi_set = c(
    "liv_stress_lcsi_1",
    "liv_stress_lcsi_2",
    "liv_stress_lcsi_3",
    "liv_stress_lcsi_4",
    "liv_crisis_lcsi_1",
    "liv_crisis_lcsi_2",
    "liv_crisis_lcsi_3",
    "liv_emerg_lcsi_1",
    "liv_emerg_lcsi_2",
    "liv_emerg_lcsi_3"
  ),
  with_hdds = FALSE,
  other_variables = c("income_v2_sum", "expenditure_food")
)

example_ipc[["ipc_table"]][1:6, 1:10]
```

```{r, eval=FALSE}
example_ipc %>%
  create_xlsx_group_x_variable(example_ipc, table_name = "ipc_table", file_path = "ipc_table.xlsx")
```


## `create_group_clusters()`

The function `create_group_clusters()` creates number of cluster and number of hh surveyed per group/strata
```{r}
create_group_clusters(
  results_table = presentresults_resultstable,
  dataset = presentresults_MSNA_template_data,
  cluster_name = "cluster_id"
) |> head()
```

## Code of Conduct

Please note that the presentresults project is released with a [Contributor Code of Conduct](https://impact-initiatives.github.io/presentresults/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
